### 2013-08-28 patchy-selection-paper.tex
added phase diagram

\newcommand{\migrate}{\lambda_\text{mig}}
\newcommand{\mutrate}{\lambda_\text{mut}}

@@

\bibliographystyle{plain}

@@

>>>>

\newcommand{\migrate}{\lambda_\text{mig}}
\newcommand{\mutrate}{\lambda_\text{mut}}
\newcommand{\Tmig}{T_\text{mig}}
\newcommand{\Tmut}{T_\text{mut}}

@@

\bibliographystyle{plainnat}

@@

One way to visualize this is by a phase diagram.
In figure \ref{fig:phase_diagram},
we give a contour plot for the time until adaptation by migration ($\Tmig = 1/\migrate$) and by new mutation ($\Tmut=1/\mutrate$)
as a function of population density, mutation rate, and distance between patches (scaled by $\sqrt{s_m}/\sigma$).

\begin{figure}[ht]
  \begin{center}
    \includegraphics{phase-diagram-log}
  \end{center}
  \caption{
  Mean time until adaptation in a new patch occurs by migration ($\Tmig$, blue) or by mutation ($\Tmut$, red),
  as a function of population density ($\rho$), mutation rate ($\mu$), 
  and distance to an already adapted patch ($R$), scaled by $\sqrt{s_m}/\sigma$.
  Note that population density and mutation rate are shown on a log scale.
  \plr{fix axis labels}
  \label{fig:phase_diagram}
  }
\end{figure}
